### 2014-12-06 Draft/evaluation.tex
updated table structure

\caption{Evaluation Results}

\begin{tabular}{lcccccccccccc}
\topline
\headcol API & Mtds & Sen & Sen$_C$ & Sen$_{ICON}$ & TP & FP & FN & P(\%) & R(\%) & F$_S$(\%) & Spec$_{ICON}$ & Acc(\%)\\
\midline 
java.io & 662 & 2417 & 78 & 88 & 57 & 31 & 21 & 64.8 & 73.1 & 68.8 & 56 & 71.8\\ 
\rowcol \amazonAPI & 51 & 1492 & 12 & 12 & 8 & 4 & 4 & 66.7 & 66.7 & 66.7 & 7 & 58.3\\ 
\paypalAPI & 33	&	151 &  20 &  &  &  &  & &  &  &  & \\ 
\rowcol Total & 746 & 4060 & 90 & 100 & 65 & 35 & 25 & 65.0$^*$ & 72.2$^*$ & 68.4$^*$ & 63 & 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{13}{p{6.5in}}{\small
$^*$ Column average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences;
Sen$_{ICON}$: Total no. of constraint Sentences identified by \tool; 
TP: Total no. of True Positives; FP: Total no. of False Positives; FN: Total no. of False Negatives;
P: Precision; R: Recall; F$_S$: F-Score; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

>>>>

\caption{Evaluation Results (Identification)}

\begin{tabular}{rlccccccccc}
\topline
\headcol S. No. & Trainer	& P$_{wrd}$	& R$_{wrd}$	& F$_{wrd}$	& P$_{ftr}$	& R$_{ftr}$	& F$_{ftr}$	& P$_{\Delta}$	& R$_{\Delta}$	& F$_{\Delta}$	\\
\midline 
		 1 		& 				& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\rowcol  2		& \amazonAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
		 3		& \paypalAPI 	& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\rowcol 		& Average 		& 662 	& 2417 		& 78 		& 88 		& 57 		& 31 		& 21 			& 64.8 			& 73.1 			\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{11}{p{6.5in}}{\small
All values are average over 10-fold cross validation;
P: Precision; R: Recall; F: F-Score;
$_{wrd}$: No features used for training;
$_{ftr}$: features used for training;
$_{\Delta}$: improvement factor ($_{ftr}$ - $_{wrd}$)} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table*}

\begin{table}
\begin{center}

\caption{Evaluation Results (Inference)}

\begin{tabular}{lccccc}
\topline
\headcol 	API 		& Mtds 	& Sen 	& Sen$_C$ 	& Spec$_{ICON}$ 	& Acc(\%)\\
\midline 
			java.io 	& 662 	& 2417 	& 78 		& 56 				& 71.8\\ 
\rowcol 	Amazon S3 REST 	& 51 	& 1492 	& 12		& 7 				& 58.3\\ 
			Paypal REST 	& 33	& 151 	& 20 		& 					& \\ 
\rowcol 	Total 		& 746 	& 4060 	& 90		& 63 				& 70.0$^*$\\ 
\bottomlinec
%----------------- END TABLE DATA ------------------------ 
\multicolumn{6}{p{3.25in}}{\small
$^*$ Average;
Mtds: Total no. of Methods; Sen: Total no. of Sentences; Sen$_C$: Total no. of constraint Sentences; Acc: Accuracy
Spec$_{ICON}$: Total no. of temporal constraint correctly identified by \tool;
} \\ 
\end{tabular}
\label{tab:results}
\end{center}
\end{table}
